%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://linkedin.com/in/tanya-sonker}{\Large Tanya Sonker}} & Email : \href{mailto:tsonker@scu.edu}{tsonker@scu.edu}\\
  \href{https://tanya-sonker.github.io/}{\color{blue}{https://tanya-sonker.github.io}} & GitHub : \href{https://github.com/tanya-sonker}{\color{blue}{tanya-sonker}} \\
 
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Santa Clara University}{Santa Clara, CA}
      {Bachelor of Science in Computer Science}{Expected June 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Fabric}{Sunnyvale, CA}
      {Software Engineer Intern}{June 2019 -- Aug 2019}
      \resumeItemListStart
        \resumeItem{}
          {Rebuilt open-source project \href{https://microservices-demo.github.io/}{\color{blue}{Sock Shop}}, a microservices demo web application, for a container security startup in stealth mode backed by The Fabric.
          }
        \resumeItem{}
          {Redesigned UI elements and developed the front-end of the revamped demo.}
        \resumeItem{}{Improved the demo by designing and implementing text receipt functionality using the Twilio API.}
        \resumeItem{}{Debugged to eliminate critical security vulnerabilities in package dependencies.}
        \resumeItem{}{Added support for SQL injection vulnerability.}
        \resumeItem{}{Built and maintained codebase on GitHub; Distributed container images on Docker Hub.}
      \resumeItemListEnd

    \resumeSubheading
      {Santa Clara University}{Santa Clara, CA}
      {Computer Science Teaching Assistant}{Jan 2018 -- June 2019}
      \resumeItemListStart
        \resumeItem{}
          {Taught programming concepts and helped debug about 15 students' C++ code every lab session.}
        \resumeItem{}
          {Weekly met with and aided Dr.  \href{https://math.scu.edu/~linnell/}{\color{blue}{Natalie Linnell}} and another TA with CSCI 60 [Object Oriented Programming] and CSCI 10 [Introduction to C++] labs.
          }
        \resumeItem{}
          {All SCU undergraduate courses are taught solely by faculty and so, students can only be hired as Lab Teaching Assistants.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Santa Clara Laptop Orchestra (SCLOrk)}{Santa Clara, CA}
      {Computer Musician}{Jan 2018 -- Present}
      \resumeItemListStart
        \resumeItem{} {Code synth definitions and experiment with as well as live code algorithmic compositions in SuperCollider to perform electronic music pieces for school's Laptop Orchestra (\href{https://www.youtube.com/watch?v=UorZXvhU6uI}{\color{blue}{SCLOrk}}).}
        \resumeItem{}{1 of 4 students chosen to be in Dr.  \href{https://works.bepress.com/bruno-ruviaro/about/}{\color{blue}{Bruno Ruviaro}}'s pilot program to extend SCLOrk's performance from one quarter on-campus to the entire academic year and off-campus.} \resumeItem{} {Collaborate with Google developers and local musicians on compositions.}
        \resumeItem{} {Diversify ensemble by referring prospective female ensemble members.}
      \resumeItemListEnd

%-----------PROJECTS-----------------
\section{Projects} 
    \resumeSubheading{R F Kennedy Elementary School}{San Jose, CA}
    {Sound Design Workshop Creator}{Feb 2019}
        \resumeItemListStart
        \resumeItem{}{Developed and conducted a workshop on Granular Sampling with 24 of R F Kennedy Elementary's 5th and 6th graders.}
        \resumeItem{} {Created the   \href{https://github.com/tanya-sonker/sound-design-workshop}{\color{blue}{code}} for each sample which included creating a synth definition to load audio samples and Pbindefs to define parameters to control aspects of samples like playback rate, duration, etc. }  
        \resumeItem{} {Developed workshop to adapt to restraints introduced by a lower socio-economic environment such as a lack of computer literacy, loudspeakers, headphones, and strong internet connection.}
  \resumeItemListEnd



%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeItemListStart
   \resumeItem{}{
     \textbf{Languages}{: Proficient in C++, SuperCollider; experience with: HTML, CSS, JavaScript, Golang; previously used: C, Java, Python, Scala; familiar with: MySQL, LaTex}
     }
     \resumeItem{}{
     \textbf{Technologies}{: Experience with: Node.js, Bootstrap, Docker, Git, MongoDB; familiar with: Kubernetes}
   }
 \resumeItemListEnd

\section{Awards}
    \resumeItemListStart
\resumeItem{}{Awarded the competitive student scholarship (full-ride) to attend the \href{https://ghc.anitab.org/2019-student-academic/scholarships/} {\color{blue}Grace Hopper Celebration} 2019.}
  \resumeItemListEnd
%-------------------------------------------
\end{document}