%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Tanya}{Sonker}{ %\urlstyle{same}\url{http://debarghyadas.com} \\
\href{mailto:tsonker@scu.edu}{tsonker@scu.edu} | 408.759.0023
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Santa Clara University}
\descript{BSc in Computer Science}
\location{Expected June 2020 | Santa Clara, CA}
Emphasis in Software \\
College of Arts and Sciences
\sectionsep


%\descript{BS in Computer Science}
%\location{Expected May 2014 | Ithaca, NY}
%Conc. in Software Engineering \\
%College of Engineering \\
%Dean's List (All Semesters) \\
%\location{ Cum. GPA: 3.92 / 4.0 \\
%Major GPA: 3.94 / 4.0}
%\sectionsep

\subsection{Jamnabai Narsee  \\ 
International School}
\descript{International Baccalaureate}
\location{Grad. June 2016 |  Mumbai, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient:}
C++ \textbullet{}  SuperCollider \\
\location{Working Experience:}
HTML \textbullet{}  CSS  \textbullet{} JavaScript \textbullet{} 
Node.js \\
\textbullet{} Go \textbullet{} Docker \textbullet{}
C \textbullet{} Git \textbullet{} Python \\
\textbullet{} Java \textbullet{} Scala \\
\location{Familiar:}
\textbullet{} MySQL \textbullet{} \LaTeX\ \textbullet{} Kubernetes 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Computer Science}
Experimental Sound Design in SuperCollider \\
Santa Clara Laptop Orchestra \\
Programming Languages \\
Theory of Algorithms \\
Data Structures \\
Object Oriented Programming \\
{\footnotesize \textit{\textbf{(Teaching Assistant)}}}\\
Introduction to C++ \\
{\footnotesize \textit{\textbf{(Former Teaching Assistant)}}}
\sectionsep

\subsection{Mathematics}
Probability + Statistics \\
Discrete Mathematics \\
Linear Algebra \\
Calculus \\
\sectionsep

\subsection{Engineering}
Community-Based Engineering Design\\
STEM Outreach in the Community \\
Computer Networks \\
Introduction to Embedded Systems \\
Introduction to Logic Design 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
GitHub://  \href{https://github.com/tanya-sonker}{\custombold{tanya-sonker}} \\
LinkedIn://  \href{https://www.linkedin.com/in/tanya-sonker}{\custombold{tanya-sonker}} \\
SCCode://  \href{https://sccode.org/tsonker}{\custombold{tsonker}} \\
% Odyssey://  \href{https://www.theodysseyonline.com/user/@tanyasonker}{\custombold{tanyasonker}} \\
Maker://  \href{https://tsonker.wixsite.com/efolio}{\custombold{efolio}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Software Engineer Intern}
\descript{| The Fabric}
\location{June 2019 - Present | Santa Clara, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Rebuilding an \href{https://microservices-demo.github.io/}{\custombold{existing}} microservices demo web application for a Cloud/IoT security startup in stealth mode backed by \href{http://www.thefabricnet.com/}{\custombold{The Fabric}}.
\item Redesigned UI elements and developed the front-end of the \href{https://github.com/tanya-sonker/KupcakeShop}{\custombold{revamped demo}}. 
\item Improved the demo by designing and implementing text receipt functionality using the Twilio REST API.
\item Debugged to eliminate high/critical security vulnerabilities and minimize low  security vulnerabilities in package dependencies.
\item Working with this open-source project required knowledge of web development and related frameworks, microservices, HTTP protocols, Go, Docker, and Git.
\end{tightemize}
\sectionsep

\runsubsection{CS Teaching Assistant}
\descript{| Santa Clara University}
\location{Jan 2018 - June 2019 | Santa Clara, CA}
\begin{tightemize}\item Taught programming concepts and helped debug about 15 students' C++ code every lab session. \item Weekly met with and aided Dr.  \href{https://math.scu.edu/~linnell/}{\custombold{Natalie Linnell}} and another TA with CSCI 60 [Object Oriented Programming] and CSCI 10 [Introduction to C++] labs.
\item All SCU undergraduate courses are taught solely by faculty and so, students can only be hired as Lab Teaching Assistants.
\end{tightemize}
\sectionsep

\runsubsection{Sound Designer}
\descript{| Santa Clara Laptop Orchestra}
\location{Jan 2018 - Present | Santa Clara, CA}
\begin{tightemize}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Code synth definitions and experiment with and live code algorithmic compositions in SuperCollider to perform electronic music pieces for school's Laptop Orchestra [ \href{https://www.youtube.com/watch?v=UorZXvhU6uI}{\custombold{SCLOrk}}] \item 1 of 4 students chosen to be in Dr.  \href{https://works.bepress.com/bruno-ruviaro/about/}{\custombold{Bruno Ruviaro}}'s pilot program to extend \href{https://www.youtube.com/watch?v=UorZXvhU6uI}{\custombold{SCLOrk}}'s performance from one quarter on-campus to the entire academic year and off-campus. \item Collaborate with Google developers and local musicians on compositions.\item Diversify ensemble by referring prospective female ensemble members. \end{tightemize}
% removed sectionsep
\section{Projects}
\runsubsection{Sound Design Workshop Creator}
\descript{| R F Kennedy Elementary}
\location{Feb 2019 | San Jose, CA}
\begin{tightemize}
\item Developed and conducted a workshop on Granular Sampling with 24 of R F Kennedy Elementary's 5th and 6th graders.  
\item Created the   \href{https://github.com/tanya-sonker/sound-design-workshop}{\custombold{code}} for each sample which included creating a synth definition to load audio samples and Pbindefs to define parameters to control aspects of samples like playback rate, duration, etc.   
\item Developed workshop to adapt to restraints introduced by a lower socio-economic environment such as a lack of computer literacy, loudspeakers, headphones, and strong internet connection.
\end{tightemize}
\sectionsep

\runsubsection{Maker}
\descript{| Rocketship Mosaic Elementary School}
\location{Jan 2018 - Apr 2018 | San Jose, CA}
\begin{tightemize}
\item Led Research and Development in a team of three to build a \href{https://littlefreelibrary.org}{\custombold{Little Free Library}}(public bookcase) for a school which lacked a library.
\item Designed and built components and interior build of the library by studying comparative models available on the market and assisted in prototyping in CAD.
\end{tightemize}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INVOLVEMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Engineering Projects}


% \runsubsection{The Odyssey Online}
% \descript{| Content Creator}
% \location{Nov 2017 - Present | Santa Clara, CA}
% \begin{tightemize}
% \item Create content focused on mental health and social justice for an online publication.
% \end{tightemize}

\end{minipage} 
\end{document}